### 2019-09-16 sections/language.tex
Last corrections for camera ready
merge remote-tracking branch 'origin/ppdp2019' into ppdp2019

Typing rules are of the form $\RelationT$, which should be read as \enquote{in environment $\Gamma$ and store typing $\Sigma$, expression $e$ has type $\tau$}.
Typing rules for expressions in the host language are presented in the appendix.
The typing rules for pretasks are given in \cref{fig:typing-rules}.
Most typing rules lift the type of their subexpressions into the $\Task$-type.
The typing rules for steps make sure the continuations $e_2$ are functions which accept a well-typed value from the left hand side (\refrule{T-Then}, \refrule{T-Next}).
References, and therefore shared editors, can only be of a basic type so they do not introduce implicit recursion (\refrule{T-Update}).

@@

Programs in \TOPHAT model interactive workflows.
Interaction means communication with end users.
End users should be able to enter information into the system, change it, clear it, reenter it, and so on.
To do this, we introduce the concept of \emph{editors}.
%
Editors are typed containers that either hold a value or are empty.
Editors that have a value can be \emph{changed}.
Empty editors can be \emph{filled}.

% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\columnwidth,page=3]{figures/drawings-crop.pdf}
%   \caption{
%     Possible states of an editor and its transitions.
%     Shared editors cannot be cleared.
%   }
%   \label{fig:editor-state}
% \end{figure}

>>>>

Typing rules are of the form $\RelationT$, which should be read as \enquote{in environment $\Gamma$ and store typing $\Sigma$, expression $e$ has type $\tau$}.
Typing rules for expressions in the host language are presented in the appendix\footnote{\url{https://github.com/timjs/tophat/appendix.pdf}}.
The typing rules for pretasks are given in \cref{fig:typing-rules}.
Most typing rules lift the type of their subexpressions into the $\Task$-type.
The typing rules for steps make sure the continuations $e_2$ are functions which accept a well-typed value from the left hand side (\refrule{T-Then}, \refrule{T-Next}).
References, and therefore shared editors, can only be of a basic type so they do not introduce implicit recursion (\refrule{T-Update}).

@@

Programs in \TOPHAT model interactive workflows.
Interaction means communication with end users.
End users should be able to enter information into the system, change it, clear it, reenter it, and so on.
To do this, we introduce the concept of \emph{editors}.
%
Editors are typed containers that either hold a value or are empty.
Editors that have a value can be \emph{changed}.
Empty editors can be \emph{filled}.
This is depicted as a state diagram in \cref{fig:editor-state} below.

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth,page=3]{figures/drawings-crop.pdf}
  \caption{
    Possible states of an editor and its transitions.
    Shared editors cannot be cleared.
  }
  \label{fig:editor-state}
\end{figure}
